An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2016-10-03 nips_2016.tex
Sent draft to Haoyu. Looks ready for arxiv i hope

\author{
  John Canny, Haoyu Chen, Daniel Seita, Xinlei Pan \\
  University of California, Berkeley \\
  \texttt{\{canny,haoyuchen,seita,xinleipan\}@berkeley.edu}
 }

@@

In practice, it is difficult to compute multinomial probabilities for large $n$,
in that case the per-bin distributions are well-approximated by Poisson
distributions with parameter $\lambda_i=P_i n$. Given a set of samples $\Theta =
\{\theta_1,\ldots,\theta_T\}$, let $c_j$ denote the number of individual samples
$\theta_i$ that fall in bin $j$ out of $N_{\rm bins}$ total. We omit bins in
which either the source or MCMC-generated distributions did not have a single
sample, resulting in the set of (at most $N_{\rm bins}$) bins $B$. Then the log
probability for the set of samples is approximated as
\begin{equation}\label{eq:log_prob_poissons}
    %\log p(\Theta) \approx \frac{1}{N_{\rm bins}} \sum_{j=1}^{N_{\rm bins}} c_j \log (n P_j) - n P_j - \log(\Gamma(c_j+1)).
    \log p(\Theta) \approx \sum_{j \in B} c_j \log (n P_j) - n P_j - \log(\Gamma(c_j+1)).
\end{equation}
The results for each model are shown in Table~\ref{tab:poissons}.

>>>>

\author{
  Haoyu Chen, Daniel Seita, Xinlei Pan, John Canny \\
  University of California, Berkeley \\
  \texttt{\{haoyuchen,seita,xinleipan,canny\}@berkeley.edu}
 }

@@

In practice, it is difficult to compute multinomial probabilities for large $n$,
in that case the per-bin distributions are well-approximated by Poisson
distributions with parameter $\lambda_i=P_i n$. Given a set of samples
$\{\theta_1,\ldots,\theta_T\}$, let $c_j$ denote the number of individual samples
$\theta_i$ that fall in bin $j$ out of $N_{\rm bins}$ total. Then we have
\begin{equation}\label{eq:log_prob_poissons}
    \log p(c_1, \ldots, c_{N_{\rm bins}} \mid P_1, \ldots, P_{N_{\rm bins}}) = \sum_{j=1}^{N_{\rm bins}} c_j \log (n P_j) - n P_j - \log(\Gamma(c_j+1)).
\end{equation}
The results for each model are shown in Table~\ref{tab:poissons}.
